WIDS 2024 Final Project

### 2024-01-12 Code/R FIle.qmd
created graph for regression

Regression between percent collective bargaining and party state average
```{r}
decade_region <- list(
  c("1980s", "Northeast"),
  c("1980s", "West"),
  c("1980s", "North Central"),
  c("1980s", "South"),
  c("2010s", "Northeast"),
  c("2010s", "West"),
  c("2010s", "North Central"),
  c("2010s", "South")
)

@@

CB_party_regression <- full_join(CB_party_regression, CB_party_temp,
                                   by = join_by(Reggression_Run, Decade, Region, Estimate, `Std. Error`, `t value`, `Pr(>|t|)`))

CB_party_regression |>
  filter(Reggression_Run == "percent_collective_bargain")
```

>>>>

t test between union and non union wages
```{r}
# 1980s
full_ntl_data_1980s <- full_ntl_data |>
  filter(decade == "1980s")
t.test(full_ntl_data_1980s$union_wage_2020_adj, full_ntl_data_1980s$nonunion_wage_2020_adj)

# 2010s
full_ntl_data_2010s <- full_ntl_data |>
  filter(decade == "2010s")
t.test(full_ntl_data_2010s$union_wage_2020_adj, full_ntl_data_2010s$nonunion_wage_2020_adj)
```

Linear regression of percent collective bargaining and party state average
```{r}
decade_region <- list(
  c("1980s", "Northeast"),
  c("1980s", "West"),
  c("1980s", "North Central"),
  c("1980s", "South"),
  c("2010s", "Northeast"),
  c("2010s", "West"),
  c("2010s", "North Central"),
  c("2010s", "South")
)

@@

CB_party_regression <- full_join(CB_party_regression, CB_party_temp,
                                   by = join_by(Reggression_Run, Decade, Region, Estimate, `Std. Error`, `t value`, `Pr(>|t|)`)) |>
  filter(Reggression_Run == "percent_collective_bargain") |>
  rename(P_Value = "Pr(>|t|)")
```

Graph of regression estimate by decade and year
```{r}
ggplot(CB_party_regression, aes(x = Decade, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity", position = "dodge", color = ifelse(CB_party_regression$P_Value > 0.05, "black", NA), size = 0.2) +
  theme_minimal() +
  labs(title = "Linear Regression Estimate by Decade",
       subtitle = "Model of Percent Collective Bargaining vs Proportion of House Delegation That is Democratic")
```
